Invariant Representations for Noisy Speech Recognition

### 2016-12-01 poster.tex
Make table prettier

    Average word error rate (WER\%) on Aurora-4 dataset on all test conditions,
        including seen and unseen noise and unseen microphone. First column
        is the number of noise conditions used for the training. The last row is a 
        preliminary experiment with layer-wise pre-training close to state-of-the-art
        model and a corresponding invariance training starting with a pretrained model.
\begin{table}
    \centering
    \label{tab:results}
    \begin{tabular}{r|rr||rr|rr|rr|rr}
        Noise       &&&  \multicolumn{2}{c|}{A} & \multicolumn{2}{c|}{B} & \multicolumn{2}{c|}{C} & \multicolumn{2}{c}{D}\\
        cond  & Inv & BL &  Inv & BL & Inv & BL & Inv & BL & Inv & BL\\
    \hline
    1           &\textcolor{dblue}{16.36}        &18.14 & 6.54  & 7.57    &12.71& 14.09   & 11.45&   13.10    & 22.47 &   24.80    \\
        2           &\textcolor{dblue}{15.56}        &17.39 & 5.90  & 6.58    &   11.69   &13.28   &11.12   &13.51   &21.79   &23.96 \\
        3           &\textcolor{dblue}{14.24}        &14.67 & 5.45  & 5.08    &   10.76&   12.44&   9.75&    9.84 &   19.93&   19.30\\
        4           &\textcolor{dblue}{13.61}        &13.84 & 5.08  & 5.29    &9.73    &9.97    &9.49    &9.56    &19.49   &19.90\\         
        5           &13.41        &\textcolor{dblue}{13.02} & 5.12  & 5.34    &9.52    &9.42    &9.55    &8.67    &19.33   &18.65\\         
        6           &12.62        &\textcolor{dblue}{12.60} & 4.80  & 4.61    &9.04    &8.86    &8.76    &8.59    &18.16   &18.21\\
    \hline\hline
    6*          &\textcolor{dblue}{11.85}        &11.99 &4.52    &4.76    &8.76    &8.76    &7.79    &8.57    &16.84&    16.99
    \end{tabular}
\end{table}
\end{block}

>>>>

    Average word error rate (WER\%) on Aurora-4 dataset on all test conditions,
        including seen and unseen noise and unseen microphone. First column
        is the number of noise conditions used for the training. The last row is a 
        preliminary experiment with layer-wise pre-training close to state-of-the-art
        model and a corresponding invariance training starting with a pretrained model.
\begin{table}
    \centering
    \label{tab:results}
    \begin{tabular}{r|rr||rr|rr|rr|rr}
        Noise       &\multicolumn{2}{c||}{AVG}&  \multicolumn{2}{c|}{A} & \multicolumn{2}{c|}{B} & \multicolumn{2}{c|}{C} & \multicolumn{2}{c}{D}\\
        cond  & Inv & BL &  Inv & BL & Inv & BL & Inv & BL & Inv & BL\\
    \hline
    1           &\textcolor{dblue}{16.36}        &18.14 & 6.54  & 7.57    &12.71& 14.09   & 11.45&   13.10    & 22.47 &   24.80    \\
        2           &\textcolor{dblue}{15.56}        &17.39 & 5.90  & 6.58    &   11.69   &13.28   &11.12   &13.51   &21.79   &23.96 \\
        3           &\textcolor{dblue}{14.24}        &14.67 & 5.45  & 5.08    &   10.76&   12.44&   9.75&    9.84 &   19.93&   19.30\\
        4           &\textcolor{dblue}{13.61}        &13.84 & 5.08  & 5.29    &9.73    &9.97    &9.49    &9.56    &19.49   &19.90\\         
        5           &13.41        &\textcolor{dblue}{13.02} & 5.12  & 5.34    &9.52    &9.42    &9.55    &8.67    &19.33   &18.65\\         
        6           &12.62        &\textcolor{dblue}{12.60} & 4.80  & 4.61    &9.04    &8.86    &8.76    &8.59    &18.16   &18.21\\
    \hline\hline
    6*          &\textcolor{dblue}{11.85}        &11.99 &4.52    &4.76    &8.76    &8.76    &7.79    &8.57    &16.84&    16.99
    \end{tabular}
\end{table}
\end{block}
